\Rpackage{MSnbase} input/output capabilities

### 2011-09-29 inst/doc/MSnbase-io/MSnbase-io.Rnw
typo in io vignette
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@58522 bc3139a8-67e5-0310-9ffc-ced21a209358
rephrasing in io vignette
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@58554 bc3139a8-67e5-0310-9ffc-ced21a209358

\Rpackage{MSnbase}'s aims are to facilitate the reproducible analysis of 
mass spectrometry data within the \R environment, from raw data import and processing, 
feature quantification, quantification and statistical analysis of the results.
Several input functions are provided to allow execution of all of several 
of these steps. Intermediate or final results can also be saved or exported. 
These capabilites are presented below.

@@

\begin{figure}[!htb] %% input
  \begin{center}
    \begin{tikzpicture}[node distance = 2cm, auto]
      % Place nodes
      \node [input] (raw) {Raw data in and open \texttt{XML} format};
      \node [fun, left of=raw, node distance=4cm] (readMSData) {\Rfunction{readMSData}};
      \node [input, below of=raw] (mgf) {Peak list in \texttt{mgf} format};
      \node [fun, left of=mgf, node distance=4cm] (readMgfData) {\Rfunction{readMgfData}};
      \node [input, below of=mgf] (spreadsheet) {Quantitation data as a spreadsheet};
      \node [fun, left of=spreadsheet, node distance=4cm] (readMSnSet) {\Rfunction{readMSnSet}};
      \node [obj, left of=readMSData, yshift=-2.5mm, node distance=4cm] (MSnExp) {\Robject{MSnExp}};
      \node [obj, left of=readMSnSet, node distance=4cm] (MSnSet) {\Robject{MSnSet}};
      \node [fun, below of=MSnExp] (quantify) {\Rfunction{quantify}};
      % Background
      \begin{pgfonlayer}{background}
        \node [fill=yellow!20,rounded corners, draw=black!50, dashed, fit=(MSnExp) (quantify) (MSnSet)] {};
      \end{pgfonlayer}
      % Draw edges
      \draw  (raw) -- (readMSData);
      \draw  (mgf) -- (readMgfData);
      \draw  (spreadsheet) -- (readMSnSet);
      \draw [->] (readMSData) -- (MSnExp);
      \draw [->] (readMgfData) -- (MSnExp);
      \draw [->] (readMSnSet) -- (MSnSet);
      \draw  (MSnExp) -- (quantify);
      \draw [->] (quantify) -- (MSnSet);
    \end{tikzpicture}
    \caption{Illustration of \texttt{MSnbase} input capabilities. 
      The white and red boxes represent \R functions/methods and objects respectively. 
      The blue boxes represent different disk storage formats.}
    \label{fig:input}
  \end{center}
\end{figure}

@@

\begin{figure}[!htb] %% out
  \begin{center}
    \begin{tikzpicture}[node distance = 2cm, auto]
      % Place nodes
      \node [input] (raw) {Raw data in and open \texttt{XML} format};
      \node [input, below of=raw] (mgf) {Peak list in \texttt{mgf} format};
      \node [fun, right of=mgf, node distance=4cm, yshift=1cm] (writeMgfData) {\Rfunction{writeMgfData}};
      \node [input, below of=mgf] (spreadsheet) {Quantitation data as a spreadsheet};
      \node [fun, right of=spreadsheet, node distance=4cm] (writeexprs) {\Rfunction{write.exprs}};

>>>>

\Rpackage{MSnbase}'s aims are to facilitate the reproducible analysis of 
mass spectrometry data within the \R environment, from raw data import and processing, 
feature quantification, quantification and statistical analysis of the results.
Data import functions for several formats are provided and intermediate or final 
results can also be saved or exported. 
These capabilites are presented below.

@@

\begin{figure}[!htb] %% input
  \begin{center}
    \begin{tikzpicture}[node distance = 2cm, auto]
      % Place nodes
      \node [input] (raw) {Raw data in an open \texttt{XML} format};
      \node [fun, left of=raw, node distance=4cm] (readMSData) {\Rfunction{readMSData}};
      \node [input, below of=raw] (mgf) {Peak list in \texttt{mgf} format};
      \node [fun, left of=mgf, node distance=4cm] (readMgfData) {\Rfunction{readMgfData}};
      \node [input, below of=mgf] (spreadsheet) {Quantitation data as a spreadsheet};
      \node [fun, left of=spreadsheet, node distance=4cm] (readMSnSet) {\Rfunction{readMSnSet}};
      \node [obj, left of=readMSData, yshift=-2.5mm, node distance=4cm] (MSnExp) {\Robject{MSnExp}};
      \node [obj, left of=readMSnSet, node distance=4cm] (MSnSet) {\Robject{MSnSet}};
      \node [fun, below of=MSnExp] (quantify) {\Rfunction{quantify}};
      % Background
      \begin{pgfonlayer}{background}
        \node [fill=yellow!20,rounded corners, draw=black!50, dashed, fit=(MSnExp) (quantify) (MSnSet)] {};
      \end{pgfonlayer}
      % Draw edges
      \draw  (raw) -- (readMSData);
      \draw  (mgf) -- (readMgfData);
      \draw  (spreadsheet) -- (readMSnSet);
      \draw [->] (readMSData) -- (MSnExp);
      \draw [->] (readMgfData) -- (MSnExp);
      \draw [->] (readMSnSet) -- (MSnSet);
      \draw  (MSnExp) -- (quantify);
      \draw [->] (quantify) -- (MSnSet);
    \end{tikzpicture}
    \caption{Illustration of \texttt{MSnbase} input capabilities. 
      The white and red boxes represent \R functions/methods and objects respectively. 
      The blue boxes represent different disk storage formats.}
    \label{fig:input}
  \end{center}
\end{figure}

@@

\begin{figure}[!htb] %% out
  \begin{center}
    \begin{tikzpicture}[node distance = 2cm, auto]
      % Place nodes
      \node [input] (raw) {Raw data in an open \texttt{XML} format};
      \node [input, below of=raw] (mgf) {Peak list in \texttt{mgf} format};
      \node [fun, right of=mgf, node distance=4cm, yshift=1cm] (writeMgfData) {\Rfunction{writeMgfData}};
      \node [input, below of=mgf] (spreadsheet) {Quantitation data as a spreadsheet};
      \node [fun, right of=spreadsheet, node distance=4cm] (writeexprs) {\Rfunction{write.exprs}};
